%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {https://www.ucl.ac.uk/prospective-students/graduate/taught/degrees/computational-statistics-machine-learning-msc}
    {MSc Computational Statistics and Machine Learning (CSML) | \textbf{Distinction}} % Degree
    {University College London (UCL)} % Institution
    {London, UK} % Location
    {Sept. 2017 - Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught by leading \emph{DeepMind} researchers including \emph{David Silver} on the \emph{Advanced Deep Learning \& Reinforcement Learning} course.}
        \item {Completed large-scale projects in NLP, reinforcement learning and machine vision, including advanced language modelling, sentence ordering for coherence, biomedical feature extraction and augmented reality tracking, using Python and TensorFlow.}
        \item {Developed a strong mathematical foundation in statistical modelling and machine learning, which I applied in my thesis and numerous projects throughout the degree, resulting in achieving the highest possible classification.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {http://www.imperial.ac.uk/study/ug/courses/aeronautics-department/aeronautical-engineering-year-abroad/}
    {MEng Aeronautical Engineering with a Year Abroad | \textbf{First Class}} % Degree
    {Imperial College London} % Institution
    {London, UK} % Location
    {Oct. 2011 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved a strong 1st class with honours (80\% average) with a final grade in the top 5\%.}
        %\item {Accredited by the \emph{RAes} and \emph{IMechE}}
        \item {Specialised in computational methods, achieving 100\% credit in \emph{Computational Fluid Dynamics} and \emph{Numerical Analysis} coursework.}
        \item {Completed my Master's thesis titled \emph{Design Synthesis of Small Unmanned Aircraft}, focusing on numerical optimisation in Matlab for appropriate selection of aerodynamic properties of an autonomous drone, resulting in a staggering 9\% weight saving of the final design.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {https://www.eng.nus.edu.sg/exchange-students/}
    {MEng Aeronautical Engineering with a Year Abroad | \textbf{First Class}} % Degree
    {National University of Singapore (NUS)} % Institution
    {Kent Ridge, Singapore} % Location
    {Aug. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved the highest ever received grade of 4.5/5.0 as the first student to be selected for this exchange programme based on academic merit.}
        \item {Self-taught Java in order to take two advanced \emph{MIT}-based modules in \emph{Programming Methodology} (A) and \emph{Data Structures and Algorithms} (A-).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}