%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {http://www.amazon.co.jp/}
    {Senior Applied Scientist | Promoted from Applied Scientist II in Jun. 2024} % Job title
    {Amazon} % Organization
    {Tokyo, Japan} % Location
    {Apr. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded \textbf{5} end-to-end ML projects that established a strategic charter in Japan, launching innovative programs and personally driving their global expansion through managing 50+ stakeholders (VP to director level) across JP, US, IN, and CN.}
        \item {Engineered production-grade pipelines using AWS leveraging orchestration, serverless processing, and real-time monitoring with solutions in Python, SQL, and Scala—to deliver scalable, end-to-end ML systems.}
        \item {Authored an influential ML paper presented at our internal conference that introduced a novel contrastive learning framework to fine-tune item embeddings within the context of \textit{replaceability}. Implementation resulted in a \textbf{26.2\%} improvement in coverage of an internal dataset.}
        \item {Trained \& validated multiple causal inference models to deliver \textbf{6M+} action recommendations to vendors across Amazon globally daily, with a combined daily potential estimate of \textbf{\$9.4B+ USD} uplift.}
        \item {Realised an annual uplift of \textbf{\$21.0M USD} through an ML-based improvement in JP address resolution, reducing failed deliveries by \textbf{81.2\%}.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {http://www.ascent.ai/en/}
    {Team Lead Research Engineer | Promoted from Research Engineer in Apr. 2019} % Job title
    {Ascent Robotics} % Organization
    {Tokyo, Japan} % Location
    {May 2017 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       % \item {Lead the \emph{Adversary} team which focused on validating the effectiveness of Ascent's autonomous vehicles over all possible scenarios through the use of simulation and advanced adversarial search techniques.}
        \item {Exposed and proposed solutions to incapabilities in the vehicle AI during simulation before proceeding to in-car testing via an array of advanced Bayesian Optimisation-based adversarial search methods in our main project as the leader of the \emph{Adversary} team.}
      % \item {Lead multiple end-to-end machine learning-based projects specifically with the goal of training our vehicles to adopt a human-like behaviour. The results of these projects have been used in publications at leading conferences worldwide.}
       % \item {Created a full end-to-end stack which clusters driving behaviours of vehicles on Japanese roads from raw 4K HD top-down drone video data. This data has been converted to an API and used in various other projects within the Adversary and vehicle AI team.}
        \item {Led a comprehensive project at Ascent Robotics that integrated 4K aerial drone footage of vehicles in diverse Japanese scenarios with advanced computer vision, tracking, and clustering techniques to produce a foundational dataset of driver behavior clusters.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {https://www.informetis.com/en/}
    {Research Engineer | UCL Master's Thesis} % Job title
    {Informetis} % Organization
    {Tokyo, Japan} % Location
    {June. 2018 - Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an optimal control policy for \emph{peak-demand} energy management as part of my Master's thesis at at \emph{UCL}, employing reinforcement learning (PPO) to strategically shift consumer demand and optimise battery storage.}
        \item {Achieved perfect peak-shifting, reducing energy consumption and utility costs by over \textbf{20\%}.}
        %\item {The code and full thesis is available on \href{https://github.com/KeirSimmons/RL-Optimal-Peak-Shift}{\emph{GitHub}}.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {http://www.airc.aist.go.jp/en/}
    {Machine Learning Researcher | Courtesy of the Daiwa Scholarship} % Job title
    {AI Research Center - National Institute of Advanced Industrial Science \& Technology} % Organization
    {Tokyo, Japan} % Location
    {Oct. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Earned a competitive research placement as the only non-doctorate researcher, implementing core ML algorithms—including reproducing \& fine-tuning DeepMind's Atari results.}
        \item {Led a reinforcement learning seminar designed to empower fellow researchers, fostering the application of cutting-edge ML techniques across diverse fields.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {http://www.dajf.org.uk/scholarships/daiwa-scholarship/scholars/daiwa-scholars-2015}
    {Daiwa Scholar} % Job title
    {The Daiwa Anglo-Japanese Foundation} % Organization
    {Tokyo, Japan} % Location
    {Aug. 2015 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Awarded the prestigious Daiwa Scholarship, a unique and highly competitive programme valued at approximately 11,000,000 JPY. I was selected as one of six scholars from over 1,000 candidates to represent the United Kingdom in machine learning in Japan.}
        \item {Completed an intensive language course, achieving business level fluency in Japanese (JLPT N2).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {https://www.eng.nus.edu.sg/undergraduatestudies/academics/enhancement-programmes/undergraduate-research-opportunities-programme-urop/}
    {Undergraduate Researcher} % Job title
    {National University of Singapore} % Organization
    {Kent Ridge, Singapore} % Location
    {Jan. 2014 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a custom sound pressure level meter application for Android using Java to monitor aircraft engine noise, incorporating a real-time graphical frequency analyser that meets aviation industry standards.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % link to github after porting everything...
    {Web Developer} % Job title
    {Volunteering} % Organization
    {London, UK} % Location
    {Jan. 2007 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created over 100 advanced open-source modifications in JavaScript and PHP for use with the popular message-board services \textit{Invision Power Board} and \textit{ZetaBoards}, including one that was used by over 1,000,000 people. Some have now been ported to \href{https://github.com/KeirSimmons/ZetaBoards}{\emph{GitHub}} for posterity.}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {http://aerosoc.co.uk/}
%    {Aeronautical Society Webmaster} % Job title
%    {Imperial College London} % Organization
%    {London, UK} % Location
%    {Sept. 2012 - Jul. 2013} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Overhauled the society's website through the use of PHP and JavaScript, writing efficient, concise and reusable code which was well commented and structured for ease of development. Website design changes annually.}
%      \end{cvitems}
%    }

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}